Application of Machine Learning to Predict the Optoelectronic Properties of Benzobisazoles

### 2014-07-02 paper/paper.tex
Add updates to the paper

\begin{figure}[H]
  \begin{center}
    \includegraphics[width=4in]{figures/cores.pdf}
  \end{center}
  \caption{TXY and CXY Cores}
  \label{fig:cores}
\end{figure}

@@

\begin{figure}[H]
  \begin{center}
    \includegraphics[width=4in]{figures/aryl.pdf}
  \end{center}
  \caption{Aryl Groups}
  \label{fig:Aryl}
\end{figure}

@@

Each side is then broken down into components of Aryl, X groups, and R groups. Aryl groups are indicated by the numbers 2 through 9 as seen in Figure \ref{fig:Aryl}. Aryl groups form the main chain part of the structure, they are able to extend the length of the chain and some have places for R groups (4, 5, 6, 7).

\begin{table}[H]
  \centering
  \caption{X/R-Groups}
  \begin{tabular}{lc}
    Label   & Name      \\
    \hline
    A/a     & Hydrogen  \\
    B/b     & Chlorine  \\
    C/c     & Bromine   \\
    D/d     & CN        \\
    E/e     & CCH       \\
    F/f     & OH        \\
    G/g     & SH        \\
    H/h     & $NH_2$    \\
    I/i     & $CH_3$    \\
    J/j     & Phenyl    \\
    K/k     & TMS       \\
    L/l     & $OCH_3$   \\
    *       & Spacer    \\
    \hline
  \end{tabular}
  \label{tab:xrgroups}
\end{table}

@@

X and R groups are both composed of the same set of substituents seen in Table \ref{tab:xrgroups}. X groups are the letters $A$ through $L$, and R groups are $a$ through $l$. The main difference between X and R groups is where they are placed in the chain, whereas R-Groups are placed on the Aryl group that directly proceeds them. As can be seen in Figure \ref{fig:Aryl} R-groups come in pairs of two. These groups can either be the same or different\hl{(?)}. Because there are some Aryl groups that do not allow any R-groups there is an additional spacer R-group that is designated as *. It has no effect on the structure of the molecule, it is just used as a place holder when converting the names to a feature vector.

@@

To be able to represent these structures to the computer, and consequently to the machine learning algorithms they must be vectorized.

Using this naming scheme, it is apparent that there are multiple ways that these could be converted into feature vectors for use in machine learning.

@@

\begin{equation}\label{decay}
    Value = \sum_i^n (A d_i^{-H})^{p}
\end{equation}

@@

\begin{equation}\label{decay2}
    Value = \sum_i^n \left(A \left(\frac{d_i}{M_i}\right)^{-H} \right)^{p}
\end{equation}

@@

Once all the data and feature vectors were collected, they were feed into the machine learning algorithms. For each feature vector, property, method set the methods relevant parameters were optimized (C, $\gamma$, max depth, $\alpha$, n neighbors). Then using these optimized parameters, the machine learning models were trained using k-folds for cross validation, specifically using 10 folds [CITE]. All of the results were then tabulated and compared based on their mean absolute errors (MAE) calculated as the distance the ML predicted value was from DFT calculated value. All of the machine learning calculations were done on a single consumer quad core computer.

>>>>

\begin{figure}[H]
  \begin{center}
    \includegraphics[width=4in]{figures/cores.pdf}
  \end{center}
  \caption{TXY and CXY Cores. The $R^{H1}$, $R^v$, and $R^{H2}$ positions correspond to the left chain, the two vertical chains, and the right chain respectively.}
  \label{fig:cores}
\end{figure}

@@

\begin{figure}[H]
  \begin{center}
    \includegraphics[width=4in]{figures/aryl.pdf}
  \end{center}
  \caption{List of all the Aryl Groups and their respective identifiers. The $R^1$ and $R^2$ positions list possible places for added substituents.}
  \label{fig:Aryl}
\end{figure}

@@

Each side is then broken down into components of Aryl, X groups, and R groups. Aryl groups are indicated by the numbers 2 through 9 as seen in Figure \ref{fig:Aryl}. Aryl groups form the main chain part of the structure, they are able to extend the length of the chain and some have places for R groups (4, 5, 6, 7) to allow for better tuning of the optoelectronic properties.

\begin{table}[H]
  \centering
  \caption{X/R-Groups}
  \begin{tabular}{lc}
    Label   & Name      \\
    \hline
    A/a     & Hydrogen  \\
    B/b     & Chlorine  \\
    C/c     & Bromine   \\
    D/d     & Cyano     \\
    E/e     & Alkyne    \\
    F/f     & Hydroxy   \\
    G/g     & Thiol     \\
    H/h     & Amine     \\
    I/i     & Methyl    \\
    J/j     & Phenyl    \\
    K/k     & TMS       \\
    L/l     & Methoxy   \\
    *       & Spacer    \\
    \hline
  \end{tabular}
  \label{tab:xrgroups}
\end{table}

@@

X and R groups are both composed of the same set of substituents seen in Table \ref{tab:xrgroups}. X groups are the letters $A$ through $L$, and R groups are $a$ through $l$. The only difference between X and R groups is where they are placed in the chain. R-Groups are placed on in the $R^1$ and $R^2$ positions of Aryl groups, whereas X groups on the other hand attach to the ends of chains and terminate them. As can be seen in Figure \ref{fig:Aryl} R-groups come in pairs of two. These groups can either be the same or different\hl{(?)}. Because there are some Aryl groups that do not allow any R-groups there is an additional spacer R-group that is designated as *. It has no effect on the structure of the molecule, it is just used as a place holder when converting the names to a feature vector.

@@

To be able to represent these structures to the computer, and consequently to the machine learning algorithms they must be vectorized. Fortunately, having a regular naming scheme as described is very beneficial in being able to vectorize these structures without having to account for every atom in the structure.

Using this naming scheme, there are multiple ways that these names could be converted into feature vectors for use in machine learning. \hl{more}

@@

\begin{equation}\label{decay}
    V = \sum_i^n (A d_i^{-H})^{p}
\end{equation}

@@

\begin{equation}\label{decay2}
    V = \sum_i^n \left(A \left(\frac{d_i}{M_i}\right)^{-H} \right)^{p}
\end{equation}

@@

Once all the data and feature vectors were collected, they were feed into the machine learning algorithms. For each feature vector, property, method set the methods relevant parameters were optimized (C, $\gamma$, max depth, $\alpha$, n neighbors). Then using these optimized parameters, the machine learning models were trained using k-folds for cross validation, specifically using 10 folds \hl{[CITE]}. All of the results were then tabulated and compared based on their mean absolute errors (MAE) calculated as the distance the ML predicted value was from DFT calculated value. All of the machine learning calculations were done on a single consumer quad core computer.
